Ecosystem size and complexity as extrinsic drivers of food chain length in branching ecosystems

### 2023-07-17 rmd/manuscript.Rmd
Update manuscript.Rmd

In the weak and strong omnivory motifs, different state transitions were associated with ecosystem size and complexity. Ecosystem size increased FCL primarily through additive mechanisms, facilitating the state transition of "B" $\rightarrow$ "B + P" (low productivity) or "No species" $\rightarrow$ "B + P" (high productivity), particularly with frequent disturbance (**Figure 6--7**). In contrast, insertion (i.e., the insertion of intermediate trophic species) and additive mechanisms were responsible for the effect of ecosystem complexity. With weak omnivory, the transition from "B + P" to "B + C + P" (insertion) was predominant when productivity was low (**Figure 9**). However, the additive mechanism ("No species" $\rightarrow$ "B + P") took primacy in the high productivity scenario (**Figure 9**). In the strong omnivory motif, transition patterns depended on disturbance frequency. When disturbance was rare ($p_m = 0.05$), the insertion mechanism ("B + P" $\rightarrow$ "B + C + P") drove the FCL change (**Figure 10**). As disturbance frequency increased, the primary process switched to an additive mechanism ("B" $\rightarrow$ "B + P" or "No species" $\rightarrow$ "B + P"; **Figure 10**).

>>>>

In the weak and strong omnivory motifs, different state transitions were associated with ecosystem size and complexity.
Ecosystem size increased FCL primarily through additive mechanisms, facilitating the state transition of "B" $\rightarrow$ "B + P" (low productivity) or "No species" $\rightarrow$ "B + P" (high productivity), particularly with frequent disturbance (**Figures 6 and 7**).
In contrast, insertion (i.e., the insertion of intermediate trophic species) and additive mechanisms were responsible for the effect of ecosystem complexity.
With weak omnivory, the transition from "B + P" to "B + C + P" (insertion) was predominant when productivity was low (**Figure 9**).
However, the additive mechanism ("No species" $\rightarrow$ "B + P") took primacy in the high productivity scenario (**Figure 9**).
In the strong omnivory motif, transition patterns depended on disturbance frequency.
When disturbance was rare ($p_m = 0.05$), the insertion mechanism ("B + P" $\rightarrow$ "B + C + P") drove the FCL change (**Figure 10**).
As disturbance frequency increased, the primary process switched to an additive mechanism ("B" $\rightarrow$ "B + P" or "No species" $\rightarrow$ "B + P"; **Figure 10**).
